\cvsection{Selected Press}

\textcolor{sectcol}{\textbf{HabitLab}}\\

\textbf{WIRED} - The HabitLab Browser Extension Curbs Your Time Wasted on the Web. \hfill January 2019\\
\url{https://www.wired.com/story/habitlab-browser-extension/}\\

\textbf{Lifehacker} - Prevent Procrastination With This Chrome Extension. \hfill February 2019\\
\url{https://lifehacker.com/prevent-procrastination-with-this-chrome-extension-1832723418}\\

\textbf{The New York Times} - Finding It Hard to Focus? Maybe It’s Not Your Fault. \hfill August 2018\\
\url{https://www.nytimes.com/2018/08/14/style/how-can-i-focus-better.html}\\

%\pagebreak

\textbf{Lifehacker} - Be More Mindful of the Time You Waste Online With HabitLab. \hfill August 2018\\
\url{https://lifehacker.com/be-more-mindful-of-the-time-you-waste-online-with-habit-1828118354}\\

\textbf{WIRED} - The Chrome Extensions We Can't Live Without. \hfill February 2018\\
\url{https://www.wired.com/story/best-chrome-extensions/}\\

\textbf{How-To Geek} - HabitLab Subtly Helps You Change Bad Online Habits. \hfill August 2018\\
\url{https://www.howtogeek.com/fyi/free-download-habitlab-subtly-helps-you-change-bad-online-habits/}\\

\textbf{The Stanford Daily} - HabitLab browser extension aims to help users \hfill March 2019\\
regain control of their online browsing behavior.\\
\begin{footnotesize}
\url{https://www.stanforddaily.com/2019/03/13/habitlab-browser-extension-aims-to-help-users-regain-control-of-their-online-browsing-behavior/}
\end{footnotesize}\\

\vspace{-4mm}

\textbf{Entrepreneur} - Use These Strategies to Maximize Productivity Without Inventing an Extra Weekday. \hfill May 2018\\
\url{https://www.entrepreneur.com/article/312764}\\

%\textbf{PCMag} The Best Free Google Chrome Extensions, July 2020.\\
%\url{https://www.pcmag.com/news/the-100-best-free-google-chrome-extensions}\\

%\vspace{-4mm}

\textbf{Tencent News} - (Chinese) \begin{CJK*}{UTF8}{gbsn}这款斯坦福大学的工具，让你远离加班，提升200％效率\end{CJK*} \hfill March 2019\\
\url{https://new.qq.com/omn/20190311/20190311A0BBRU.html}\\

%\pagebreak

\textcolor{sectcol}{\textbf{Crowd Research / Daemo}}\\

\textbf{Stanford University News} - A Stanford-led platform for crowdsourced research \hfill October 2017\\
gives experience to global participants\\
\url{https://news.stanford.edu/2017/10/23/crowdsourced-research-gives-experience-global-participants/}\\

\textbf{WIRED} - Amazon's Turker Crowd Has Had Enough. \hfill August 2017\\
\url{https://www.wired.com/story/amazons-turker-crowd-has-had-enough/}\\

\textcolor{sectcol}{\textbf{UNetbootin}}\\

\textbf{Forbes} - How To Try Linux Without Making Any Changes To Your PC. \hfill September 2018\\
\begin{small}
\url{https://www.forbes.com/sites/jasonevangelho/2018/09/18/how-to-safely-try-linux-on-your-mac-or-windows-pc/}
\end{small}\\

\textbf{PCWorld} - Create a Bootable Linux Flash Drive in Three Easy Steps. \hfill February 2012\\
\url{https://www.pcworld.com/article/249870/create_a_bootable_linux_flash_drive_in_three_easy_steps.html}\\

\textbf{Lifehacker} - The Complete Guide to Saving Your Windows System with a Thumb Drive. \hfill March 2010\\
\url{https://lifehacker.com/the-complete-guide-to-saving-your-windows-system-with-a-5504531}\\

%Installing Ubuntu on an old netbook with hair tearing and profanity. Network World, August 2014.\\
%\begin{footnotesize}
%\url{https://www.networkworld.com/article/2465150/installing-ubuntu-on-an-old-netbook-with-hair-tearing-and-profanity.html}
%\end{footnotesize}\\

%Linux on the NUC: Using Ubuntu, Mint, Fedora, and the SteamOS beta. Ars Technica, February 2014.\\
%\begin{small}
%\url{https://arstechnica.com/gadgets/2014/02/linux-on-the-nuc-using-ubuntu-mint-fedora-and-the-steamos-beta/}
%\end{small}\\

\textcolor{sectcol}{\textbf{Wubi}}\\

\textbf{Ars Technica} - Wubi arrives: a look at Ubuntu 8.04 alpha 5. \hfill February 2008\\
\url{https://arstechnica.com/information-technology/2008/02/wubi-arrives-a-look-at-ubuntu-8-04-alpha-5/}\\

\textbf{Lifehacker} - Install Ubuntu on a Windows Netbook, No Partitioning Needed. \hfill May 2008\\
\url{https://lifehacker.com/install-ubuntu-on-a-windows-netbook-no-partitioning-ne-5542387}\\

\textbf{PCWorld} - The Ubuntu guide for displaced Windows users. \hfill March 2013\\
\url{https://www.pcworld.com/article/2030132/the-ubuntu-guide-for-displaced-windows-users.html}\\