%\cvsection{Publications in Academic Conferences and Journals}
%\cvsection{Select Journal and Conference Papers}
\cvsection{Select Publications.}

%\textbf{Geza Kovacs}, Daniel Deutsch, Markus Freitag.
\href{https://aclanthology.org/2024.wmt-1.109.pdf}{Mitigating Metric Bias in Minimum Bayes Risk Decoding.} \emph{Proceedings of the Ninth Conference on Machine Translation (WMT). 2024.}

% {\small Mara Finkelstein, Daniel Deutsch, Parker Riley, Juraj Juraska} \textbf{Geza Kovacs}, {\small Markus Freitag.}
\href{https://arxiv.org/pdf/2411.15387}{From Jack of All Trades to Master of One: Specializing LLM-based Autoraters to a Test Set.} ICML 2025.

% {\small Daniel Deutsch, Eleftheria Briakou, Isaac Caswell, Mara Finkelstein, Rebecca Galor, Juraj Juraska,} \textbf{Geza Kovacs}, {\small Alison Lui, Ricardo Rei, Jason Riesa, Shruti Rijhwani, Parker Riley, Elizabeth Salesky, Firas Trabelsi, Stephanie Winkler, Biao Zhang, Markus Freitag.}
\href{https://arxiv.org/pdf/2502.12404}{WMT24++: Expanding the Language Coverage of WMT24 to 55 Languages \& Dialects.} ACL 2025.

% {\small Jessy Lin,} \textbf{Geza Kovacs}, {\small Aditya Shastry, Jorn Wuebker, John DeNero.}
\href{https://aclanthology.org/2022.naacl-main.36.pdf}{Automatic Correction of Human Translations.} \emph{Proceedings of the 2022 Conference of the North American Chapter of the Association for Computational Linguistics. 2022}. \textbf{Best Paper Award}, Best New Task, and Best New Resource. % \textbf{Best Paper Award} in 2 categories: Best New Task and Best New Resource.\\

% {\small Xin Liu, Daniel McDuff,} \textbf{Geza Kovacs}, {\small Isaac Galatzer-Levy, Jacob Sunshine, Jiening Zhan, Ming-Zher Poh, Shun Liao, Paolo Di Achille, Shwetak Patel.}
\href{https://arxiv.org/pdf/2305.15525}{Large Language Models are Few-Shot Health Learners.} Under review, 2025.

% {\small Isaac Caswell, Elizabeth Nielsen, Jiaming Luo, Colin Cherry,} \textbf{Geza Kovacs}, {\small Hadar Shemtov, Partha Talukdar, Dinesh Tewari, Baba Mamadi Diane, Koulako Moussa Doumbouya, Djibrila Diane, Solo Farabado Cissé.}
\href{https://arxiv.org/pdf/2502.12301}{SMOL: Professionally translated parallel data for 115 under-represented languages.} Under review, 2025.

% {\small Mike A. Merrill, Akshay Paruchuri, Naghmeh Rezaei,} \textbf{Geza Kovacs}, {\small Javier Perez, Yun Liu, Erik Schenck, Nova Hammerquist, Jake Sunshine, Shyam Tailor, Kumar Ayush, Hao-Wei Su, Qian He, Cory Y. McLean, Mark Malhotra, Shwetak Patel Jiening Zhan, Tim Althoff, Daniel McDuff, Xin Liu}
\href{https://arxiv.org/pdf/2406.06464}{Transforming Wearable Data into Health Insights using Large Language Model Agents.} Under review, 2025.

\href{https://aclanthology.org/2023.wmt-1.53.pdf}{Findings of the Word-Level AutoCompletion Shared Task in WMT 2023.} \emph{Proceedings of the Seventh Conference on Machine Translation (WMT). 2023.}

% \textbf{Geza Kovacs} {\small and John DeNero.}
\href{https://aclanthology.org/2022.amta-research.23.pdf}{Measuring the Effects of Human and Machine Translation on Website Engagement.} \emph{Proceedings of the 15th Conference of the Association for Machine Translation in the Americas (Research Track). 2022}. \textbf{Best Presentation Award.}

% {\small Francisco Casacuberta, George Foster, Guoping Huang, Philipp Koehn,} \textbf{Geza Kovacs}, {\small Lemao Liu, Shuming Shi, Taro Watanabe, Chengqing Zong.}
\href{https://aclanthology.org/2022.wmt-1.75.pdf}{Findings of the Word-Level AutoCompletion Shared Task in WMT 2022.} \emph{Proceedings of the Seventh Conference on Machine Translation (WMT). 2022.}

% {\small Samuel Läubli, Patrick Simianer, Joern Wuebker,} \textbf{Geza Kovacs}, {\small Rico Sennrich, Spence Green.}
\href{https://arxiv.org/pdf/2011.05978.pdf}{The Impact of Text Presentation on Translator Performance.} \emph{Target: International Journal of Translation Studies, 2021}.

% \textbf{Geza Kovacs}, {\small Zhengxuan Wu, Michael Bernstein.}
\href{https://hci.stanford.edu/publications/2021/notnow/notnowasklater.pdf}{Not Now, Ask Later: Users Weaken Their Behavior Change Regimen Over Time, But Expect To Re-Strengthen It Imminently.} \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2021}. Acceptance rate: 23\%. %

% \textbf{Geza Kovacs}, {\small Drew Mylander Gregory, Zilin Ma, Zhengxuan Wu, Golrokh Emami, Jacob Ray, Michael Bernstein.}
\href{https://hci.stanford.edu/publications/2019/conservation/conservation-chi2019.pdf}{Conservation of Procrastination: Do Productivity Interventions Save Time Or Just Redistribute It?} \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2019}. Acceptance rate: 23.8\%. %

%\pagebreak

% \textbf{Geza Kovacs}, {\small Zhengxuan Wu, Michael Bernstein.}
\href{https://hci.stanford.edu/publications/2018/habitlab/habitlab-cscw18.pdf}{Rotating Online Behavior Change Interventions Increases Effectiveness But Also Increases Attrition.} \emph{ACM annual conference on Computer-Supported Cooperative Work and Social Computing (CSCW) 2018}. Acceptance rate: 26\%.

% {\small Rajan Vaish, Neil Gaikwad,} \textbf{Geza Kovacs}, {\small Andreas Veit, Ranjay Krishna, Imanol Arrieta Ibarra, Camelia Simoiu, Michael Wilber, Serge Belongie, Sharad Goel, James Davis, Michael Bernstein.}
\href{https://hci.stanford.edu/publications/2017/crowdresearch/crowd-research-uist2017.pdf}{Crowd Research: Open and Scalable University Laboratories.} \emph{ACM Symposium on User Interface Software and Technology (UIST) 2017}. Acceptance rate: 22\%.

% {\small Kiley Sobel,} \textbf{Geza Kovacs}, {\small Galen McQuillen, Andrew Cross, Nirupama Chandrasekaran, Nathalie Riche, Ed Cutrell, Meredith Morris.}
\href{https://www.microsoft.com/en-us/research/wp-content/uploads/2016/10/edufeed.pdf}{EduFeed: A Social Feed to Engage Preliterate Children in Educational Activities.} \emph{ACM annual conference on Computer-Supported Cooperative Work and Social Computing (CSCW) 2017}. Acceptance rate: 35\%.

% \textbf{Geza Kovacs}.
\href{https://hci.stanford.edu/publications/2016/invideo/invideo-las2016.pdf}{Effects of In-Video Quizzes on MOOC Lecture Viewing.} \emph{ACM annual conference on Learning at Scale (L@S) 2016}. Acceptance rate: 22\%.

% \textbf{Geza Kovacs} {\small and Robert C. Miller.}
\href{http://up.csail.mit.edu/other-pubs/chi2014-smartsubs.pdf}{Smart Subtitles for Vocabulary Learning.} \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2014}. Acceptance rate: 23\%.

% \cvsection{Workshop and Demo Papers}

% {\small Stanford Crowd Research,} \textbf{Geza Kovacs}, {\small Rajan Vaish, Michael Bernstein.} ``\href{https://hci.stanford.edu/publications/2015/crowdresearch/daemo-uist.pdf}{Daemo: A Self-Governed Crowdsourcing Marketplace.}'' \emph{ACM Symposium on User Interface Software and Technology (UIST) 2015, Poster}.\\

% \textbf{Geza Kovacs}. ``\href{https://hci.stanford.edu/publications/2015/feedlearn/feedlearn-chi2015.pdf}{FeedLearn: Using Facebook Feeds for Microlearning.}'' \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2015, Extended Abstracts}.\\ % Acceptance rate: 45\%

% \textbf{Geza Kovacs}. ``\href{https://hci.stanford.edu/publications/2015/quizcram/quizcram-chi2015.pdf}{QuizCram: A Question-Driven Video Studying Interface.}'' \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2015, Extended Abstracts}.\\

% {\small Joseph Jay Williams,} \textbf{Geza Kovacs}, {\small Caren Walker, Samuel G Maldonado, Tania Lombrozo.} ``\href{https://hci.stanford.edu/publications/2014/explain/explain-chi2014.pdf}{Learning Online via Prompts to Explain.}'' \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2014, Extended Abstracts}.\\

% \textbf{Geza Kovacs} {\small and Robert C. Miller.} ``\href{http://up.csail.mit.edu/other-pubs/uist2013-mangareader.pdf}{Foreign Manga Reader: Learn Grammar and Pronunciation while Reading Comics.}'' \emph{ACM Symposium on User Interface Software and Technology (UIST) 2013, Demo}.\\

% \textbf{Geza Kovacs}. ``\href{http://up.csail.mit.edu/other-pubs/chi2013-smartsubs.pdf}{Smart Subtitles for Language Learning.}'' \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2013, Extended Abstracts}.\\ %\\
% %\url{http://groups.csail.mit.edu/uid/other-pubs/chi2013-smartsubs.pdf}

% \textbf{Geza Kovacs}. ``\href{http://up.csail.mit.edu/other-pubs/chi2012-screenshots-for-translation-context.pdf}{ScreenMatch: providing context to software translators by displaying screenshots.}'' \emph{ACM annual conference on Human Factors in Computing Systems (CHI) 2012, Extended Abstracts}.\\ %\\
% %\url{http://groups.csail.mit.edu/uid/other-pubs/chi2012-screenshots-for-translation-context.pdf}

% %\cvsection{Preprints}

